A Pilot Multicenter Cluster Randomized Trial to Compare The Effect of Trauma Life Support Training Programs on Patient and Provider Outcomes

### 2024-01-18 pilot-publication/lab-book.Rmd
Start adding trauma cohorts

```{r setup}
noacsr::source_all_functions()
load_packages()
```

@@

```{r}
## Import data
data <- readr::read_csv(Sys.getenv("DATA_DIR"))

## Prepare data
data <- prepare_data(data, codebook)

## Get variables to compare
retrospective.variables <- names(data)[grep("_r__", names(data), fixed = TRUE)]
directly.observed.variables <- retrospective.variables %>%
    stringr::str_replace_all(pattern = "\\_r\\_\\_", replacement = "\\_\\_") %>%
    stringr::str_replace_all(pattern = "\\_r$", replacement = "")

>>>>

```{r setup}
noacsr::source_all_functions()
load_packages()

## Import data
data <- readr::read_csv(Sys.getenv("DATA_DIR"))

## Prepare data
data <- prepare_data(data, codebook)
```

## Create trauma cohorts

Subgroups of men, women, blunt multisystem trauma, penetrating trauma, shock, severe traumatic brain injury, and elderly.

```{r}
# Create a function that counts the number of columns that are not 0
count_unique_regions <- function(ais.region.data) {
    unique.regions <- apply(ais.region.data, 1, function(row) {
        sum(row != 0, na.rm = TRUE)
    })
    return(unique.regions)
}

unique.regions.count <- data %>%
    select(starts_with("mxaisbr_"), -mxaisbr_General) %>%
    count_unique_regions()

# Create a function that counts the number of columns that are 3 or more
count_severe_regions <- function(ais.region.data) {
    severe.regions <- apply(ais.region.data, 1, function(row) {
        sum(row >= 3, na.rm = TRUE)
    })
    return(severe.regions)
}

severe.regions.count <- data %>%
    select(starts_with("mxaisbr_"), -mxaisbr_General) %>%
    count_severe_regions()

# Define blunt multisystem trauma
dominating.injury.type <- data$incident__dominating_injury_type
blunt.multisystem.trauma <- dominating.injury.type == "Blunt" & severe.regions.count >= 2

# Define penetrating trauma
penetrating.trauma <- dominating.injury.type == "Penetrating"

# Define shock
shock <- data$patvitals__ed_sbp < 90

# Define severe traumatic brain injury
severe.tbi <- data$patvitals__ed_gcs < 9 & data$mxaisbr_Head >= 3

# Define elderly
elderly <- data$patinfo__pt_age >= 65

# Define male
male <- data$patinfo__pt_gender == "Male"

# Define female
female <- data$patinfo__pt_gender == "Female"

cohort.data <- data.frame(
    "Blunt multisystem trauma" = blunt.multisystem.trauma,
    "Penetrating trauma" = penetrating.trauma,
    "Shock" = shock,
    "Severe TBI" = severe.tbi,
    "Elderly" = elderly,
    "Male" = male,
    "Female" = female,
    arm = data$arm
)

create_descriptive_table(cohort.data, strata = "arm", include.overall = TRUE)
```
```

@@

```{r}
## Get variables to compare
retrospective.variables <- names(data)[grep("_r__", names(data), fixed = TRUE)]
directly.observed.variables <- retrospective.variables %>%
    stringr::str_replace_all(pattern = "\\_r\\_\\_", replacement = "\\_\\_") %>%
    stringr::str_replace_all(pattern = "\\_r$", replacement = "")
